### 2016-01-19 paper.tex
Worsens --> is more pronounced

Performance curves for the rotor with both NACA 0021 and cylindrical struts are
shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
struts reduce performance dramatically, which worsens as $\lambda$ increases.
This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
though the strut losses in this case are larger due to the very high drag profile.

>>>>

Performance curves for the rotor with both NACA 0021 and cylindrical struts are
shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
struts reduce performance dramatically, which is more pronounced as $\lambda$
increases. This is in accordance with the measurements of Rawlings
\cite{Rawlings2008}, though the strut losses in this case are larger due to the
very high drag profile.
